\pdfbookmark[0]{English title page}{label:titlepage_en}
\aautitlepage{%
  \englishprojectinfo%
  {\mytitle}
  %{Scientific Theme}
  %{Fall 2014}
  %{XXX}
  {Jørgen Christian Heinsen}
  {Christian Fischer Pedersen}
  {3}
  {\handindate}
}
{\textbf{Department of Engineering}\\Aarhus University\\\href{eng.au.dk}{eng.au.dk}}
{%

This master thesis addresses the relation between dependability and adaptivity, and explores how changes to capacity and redundancy influence availability in a system optimized for resilience. Adaptivity and dependability were found to represent resilience as a correlation. By incorporating either of the four subcomponents of adaptivity, the dependability of a given system can be optimized which in turn improves the resilience of the system. A test showing how changes to capacity and redundancy of a system improve availability at high loads was designed and conducted. Three different capacity quantities were tested, showing that increased capacity indeed increases the amount of load a given system can serve, while satisfying high availability requirements.
}

\cleardoublepage
{\selectlanguage{danish}
\pdfbookmark[0]{Danish title page}{label:titlepage_da}
\aautitlepage{%
  \danishprojectinfo%
  {\mytitledk}
  %{Semestertema}
  %{Efterårssemestret 2010}
  %{XXX}
  {Jørgen Chrstian Heinsen}
  {Christian Fischer Pedersen}
  {3}
  {\handindatedk}
}
{\textbf{Institut for Ingeniørvidenskab}\\Aarhus Universitet\\\href{eng.au.dk}{eng.au.dk}
}
{%
	Dette speciale kortlægger relationen mellem pålidelighed og tlpasningsevne og udforsker, hvordan kapactitet- og redundansændringer påvirker tilgængelighed i et system optimeret for modstandsdygtigt. Tilpasningsevne og pålidelighed udgør tilsammen modstandsdygtigheden. Pålideligheden kan forstærkes ved at inkorporere tilpasningsevnen i et systemdesign.
	Korrelationen mellem på den ene side kapaciteten og redundansen og på den anden side tilgængeligheden blev bekræftet i udførelsen af et forsøg, der viste, hvordan en øget kapacitet gør det muligt at service et større antal simultane forespørgelser og samtidigt opretholde et højt niveau af tilgængelighed.
	
}
}
