\section{Problem formulation}
\label{sc:problem_formulation}

\begin{itemize}  
\item 1.a How can cloud computing be used to solve availability, performance and maintainability requirements for enterprise applications?
\item 1.b How can cloud computing be used in an enterprise application architecture?

\item 2.a How are enterprise application challenges and possible solutions affected by the application domain?
\item 2.b How does the enterprise application domain affect challenges and possible solutions?
\item 2.c How does the domain shape the challenges in a specific application architecture?
\item 2.d How does the domain and organization shape the challenges in a specific application architecture?

\item 3.a How does a distributed application architecture deal with a single point of failure?
\item 3.b How is single point of failure avoided in a distributed application architecture?

\item 3.c How is the optimal application architecture and distribution method determined and evaluated?
\item 3.d How is the enterprise application architecture determined?
\item 3.e How is the enterprise application architecture evaluated?
\end{itemize}

\subsection*{Notes}
How are the challenges and their optimal solution affected by the specific application?

What determines the optimal application architecture, database and distribution?

How is the optimal application architecture, database and distribution determined?

System architecture:
How is application data optimally stored?
How is application data optimally distributed?

How are application updates optimally executed?
How are updates 

How is the system distributed

This area has been named cloud computing, 

Big cloud computing platforms are now available, offering server rental with 

From these requirements big cloud platforms have been started, 

These requirements has started big scale initiatives in cloud computing, has generated new tools and databases available for development of distributed big scale enterprise applications. 

Creating a need for developers to explore and evaluate which of the many platforms to choose, 